---
title: ""
author: ""
date: ""
output: html_document
---

```{r}
library(tidyverse)
load("data/penguins_sep.RData") # May need to update to locate file
load("data/join_practice.RData") # May need to update to locate file
penguins_set1 = slice_sample(penguins1, n = 20)
penguins_set2 = slice_sample(penguins1, n = 20)
```

# 1. Use `pivot_longer()` to transform the data found in `table4a`.

```{r}

```

# 2. Use `pivot_wider()` to transform the data found in `table2` (specifically, the `type` column).

```{r}

```

# 3. 
##  A. Use `bind_rows()` to combine the `penguins1` and `penguins2` dfs.
##  B. Then, pipe that result to combine with `penguins3`.

```{r}

```

# 4. Using dfs `x` and `y`, write some code that will return a new df that contains only the observations common in both.

```{r}

```

# 5. Using dfs `x` and `y`, write some code that will return a new df that contains all variables across both dfs, but only from observations in `x`.

```{r}

```

# 6. Using dfs `x` and `y`, write some code that will return a new df that contains all variables across both dfs, but only from observations in `y`.

```{r}

```

# 7. Using dfs `x` and `y`, write some code that will return a new df that contains all variables and observations from both dfs.
  
```{r}

```

# 8. Using dfs `penguins_set1` and `penguins_set2`, write some code that will return a new df that contains all unique observations from both samples.

```{r}

```

# 9. Using dfs `penguins_set1` and `penguins_set2`, write some code that will return a new df that contains only the observations that appeared in both samples.

```{r}

```

# 10. Using dfs `penguins_set1` and `penguins_set2`, write some code that will return a new df that contains only the unique observations in `penguins_set1`.

```{r}

```






